% !TEX program = pdflatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jiayang Pang}

\basicInfo{
  \email{jiayangpang0408@gmail.com} \textperiodcentered\ 
  \phone{(+86) 181-5860-5586} \textperiodcentered\ 
  }

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{The Chinese University of Hong Kong, Shenzhen}{Shenzhen, China}
\textit{Bachelor of Computer Science}{Aug. 2020 – May. 2024}


\section{\faUsers\ Experience}
\datedsubsection{\textbf{FLAG Inc.} California, America}{2012 -- Present}
\role{Summer Intern}{Manager: xxx}
Brief introduction: xxx.
\begin{itemize}
  \item Implemented xxx feature
  \item Optimized xxx 5\%
  \item xxx
\end{itemize}

\datedsubsection{\textbf{xxx Projects}}{Jan. 2015 -- Present}
\role{C, Python, Django, Linux}{Individual Projects, collaborated with xxx}
Brief introduction: xxx
\begin{itemize}
  \item Implemented xxx feature
  \item Optimized xxx 5\%
  \item xxx
\end{itemize}

\datedsubsection{\textbf{\LaTeX\ résumé template}}{May. 2015 -- Present}
\role{\LaTeX, Maintainer}{Individual Projects}
An elegant \LaTeX\ résumé template, https://github.com/billryan/resume
\begin{itemize}
  \item Easy to be further customized or extended
  \item Full support for unicode characters (e.g. CJK) with \XeLaTeX\
  \item FontAwesome 4.5.0 support
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

% \section{Course}
% \begin{itemize}[parsep=0.5ex]
%   \item Blog: http://your.blog.me
%   \item GitHub: https://github.com/username
%   \item Languages: English - Fluent, Mandarin - Native speaker
% \end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Languages: C++, Python, Java, Cuda, Verilog
  \item Technology: linux, git/github, vim, Latex, CMake, Markdown, jupyter, 

\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{Undergraduate Research Awards}{Nov. 2022}
\datedline{Dean’s list}{Sep. 2022}
\datedline{\textit{\nth{2} Prize}, Award on Programming Contest of CUHKSZ }{Nov. 2021}


% \section{\faInfo\ Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
%   \item Blog: http://your.blog.me
%   \item GitHub: https://github.com/username
%   \item Languages: English - Fluent, Mandarin - Native speaker
% \end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
